API design for machine learning software: experiences from the scikit-learn project

### 2013-06-22 paper.tex
grid search doesn't work for clustering, so Rand index is irrelevant

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as inputs an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
hyper-parameter grid, which defines the values to search. Optionally, they can
also take a cross-validation scheme and a score function.  The library provides
various such cross-validation schemes, including K-Fold (default), Leave-One-Out
and Bootstrap. The score function used by default is the \texttt{score} method
provided by the estimator. However, the library provides a large variety of
score functions that the user can choose from,
including accuracy and $F_1$-score for classification;
$R^2$ score or mean squared error for regression;
and the Rand index for clustering.

>>>>

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as inputs an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
hyper-parameter grid, which defines the values to search. Optionally, they can
also take a cross-validation scheme and a score function.  The library provides
various such cross-validation schemes, including K-Fold (default), Leave-One-Out
and Bootstrap. The score function used by default is the \texttt{score} method
provided by the estimator. However, the library provides a large variety of
score functions that the user can choose from,
including accuracy, AUC, $F_1$ score (classification),
$R^2$ score and mean squared error (regression).
